\section{Initial Login}

We will restart the VM named alpha, and login for the first-time.

\subsection{First time login pages}
\begin{enumerate}
  \item In VirtualBox right-click the VM named alpha.
  \item Select Start $>$ Normal Start
  \item When the Ubuntu login window appears, login.
  \item When the desktop appears, a setup window named ``Online Accounts'' will appear.
  \item Click Skip.
  \item On the page Enable Ubutnu Pro, select Skip for Now and then click Next.
  \item On the Help Improve Ubuntu, make a choice and click Next.
  \item On the Privacy page, enable Location Services, and click Next.
  \item On the Your Ready To Go Page, click Done.
\end{enumerate}

\subsection{Screen Blank}

Until you get everything setup, it would be good to turn off the annoying screen blanking.

\begin{enumerate}
  \item In the Ubuntu desktop, got Activities $>$ Settings $>$ Privacy $>$ Screen
  \item Change Blank screen to: Never
  \item Change Automatic Screen Lock to: Disabled
  \item Change Lock Screen on Suspend to: Disabled
\end{enumerate}


\subsection{Power Auto Suspend}

Since the alpha VM is running on the laptop, it will lose connections when the laptop goes to sleep to save power.
Let's prevent this from happening.

\begin{enumerate}
  \item In the Ubuntu desktop, got Activities $>$ Settings $>$ Power
  \item Change Screen Blank to: Never
  \item Change Automatic Power Saver to: Disabled
  \item Change Automatic Suspend to: Off
\end{enumerate}


\subsection{Screen Resolution}

Finally it would be good for the alpha guest VM to make full use of the display on the laptop host.

\begin{enumerate}
  \item In the Ubuntu desktop, got Activities $>$ Settings $>$ Displays
  \item You will need to try different settings for Resolution.
  \item Click the green Apply button.
  \item If you like the resolution setting click Keep Changes, otherwise click Revert Settings.
  \item For my laptop, Resolution=1680x1050 seems to work best.
\end{enumerate}

\subsection{Shutdown}

Shutdown the alpha VM to prepare for the next section.