\section{Virtual Machine}

Setting up a Virtual Machine is not difficult, but there are many steps involved.

\subsection{Download Linux image}
To create an Ubuntu Desktop virtual machine on the VirtualBox hypervisor, we will need a distribution image.

\begin{enumerate}
  \item Browse to https://ubuntu.com/download/desktop
  \item Search the page for "check out our alternative downloads", and click it.
  \item Search the page under Past Releases for Ubuntu 22.04 LTS (Jammy Jellyfish), and click it.
  \item Click the link for "64-bit PC (AMD64) desktop image".
  \item Download of the file named ubuntu-22.04.5-desktop-amd64.iso will complete in a few minutes.
\end{enumerate}



\subsection{Create New Virtual Machine}
Let's create a new virtual machine in VirtualBox with the image we downloaded.

\begin{enumerate}
  \item From the Windows start menu, launch Oracle VirtualBox.
  \item In Oracle VirtualBox Manager application goto: Machine $>$ New... 
  \item In the Create Virtual Machine popup dialog, we'll set Name="alpha".
  \item Click the ISO Image field and search for the ubuntu-22.04.5-desktop-amd64.iso you downloaded.
  \item Set Type=Linux
  \item Set Subtype=Ubuntu
  \item Set Version=Ubuntu (64-bit)
  \item Check "Skip Unattended Installation".
  \item Expand the Hardware section.
  \item Increase Processors to 2 CPUs.
  \item Click the Finish button.
\end{enumerate}



\subsection{Start the Virtual Machine}
Okay, let's launch Ubuntu inside VirtualBox.

\begin{enumerate}
  \item In the Oracle VirtualBox Manager application, search the left panel for the machine "alpha" you just created.
  \item Right-click on "alpha" and select Start $>$ Normal Start.
  \item Once the boot screen appears in the preview pane, click "Show" on the top menu.
  \item Click inside window the boot window that appears, select "Try or Install Ubuntu", and hit enter.
\end{enumerate}

\subsection{Install Ubuntu}
Time to install Ubuntu onto the VM!

\begin{enumerate}
  \item Once the Ubuntu desktop appears, you should see a window the the title "Install".
  \item The page has two options, choose your language then select the option "Install Ubuntu".
  \item On the Keyboard Layout page, choose your keyboard layout and click "Continue".
  \item On the Updates and Other Software page, choose Minimal Installation, uncheck "Download Updates while installing Ubuntu", check "Install third-party software..."
  \item Click "Continue".
  \item On the Installation Type page, select "Erase disk and install Ubuntu".
  \item Click "Install Now".
  \item On the pop-up box that says "Write the changes to disk?", click "Continue".
  \item Select your timezone and click "Continue".
  \item On the "Who are you?" page, populate your name, set the computer name to "alpha", set your username and password.
  \item Choose "Require my password to log in".
  \item Click "Continue".
  \item Ubutnu will begin installing onto the VM, be patient it will take 10-15 minutes to complete.
  \item Once the installation has completed, click the "Restart Now" button.
  \item Wait a few moments, an Ubutnu screen will appear telling you to remove the installation media.  DO NOT Press Enter Yet!
  \item Go into the VirtualBox Manager application, select the "alpha" machine, and click Settings on the top menu.
  \item Select Storage from the Left panel.
  \item Under Controller IDE, click the disk icon.
  \item Uncheck Live CD/DVD.  Click OK.
  \item Now go back to the remove installation media screen, and press Enter.
  \item Wait for the VM to shutdown.
\end{enumerate}






