\section{SSH Service}
Most Linux \textbf{server} distributions are already setup for inbound SSH connectivity.
However, Linux \textbf{desktop} distributions are setup to support outbound SSH connections only.
The Ubuntu desktop distribution is no exception.
It is setup to be an SSH client, but not a server.
Inbound SSH support must be setup manually.

\subsection{Install SSH Server}
To install the SSH service on an Ubuntu system\footnote{https://devconnected.com/how-to-install-and-enable-ssh-server-on-ubuntu-20-04/}, open a terminal on alpha and enter the following:

\begin{verbatim}
$ sudo apt-get install openssh-server
$ systemctl status ssh

# If ssh.service is not running, do the following command:
$ sudo systemctl restart ssh
\end{verbatim}


\subsection{Initial SSH remote login}
Now that alpha has an available SSH service, let's test the connection.

\begin{itemize}
  \item On your laptop, open a Windows command shell and do the commands below.
  \item When prompted "Are you sure you want to continue connecting" enter "yes".
  \item Then enter your password for alpha.
\end{itemize}


\begin{verbatim}
C:\Users\vfinl>ssh vfinley@alpha

The authenticity of host 'alpha (192.168.56.104)' can't be established.
ED25519 key fingerprint is SHA256:YTJSyWrfm2oppwq+vtpskrQjk0hMw80dJ8xzBAfkcOI.
This key is not known by any other names.
Are you sure you want to continue connecting (yes/no/[fingerprint])? yes

Warning: Permanently added 'alpha' (ED25519) to the list of known hosts.

vfinley@alpha's password:
Welcome to Ubuntu 22.04.5 LTS (GNU/Linux 6.8.0-57-generic x86_64)

 * Documentation:  https://help.ubuntu.com
 * Management:     https://landscape.canonical.com
 * Support:        https://ubuntu.com/pro

Expanded Security Maintenance for Applications is not enabled.

0 updates can be applied immediately.
\end{verbatim}


\subsection{Check BASH shell response}

Congratulations, you are SSH'd into alpha!
To verify everything is working, enter "ls" at the BASH shell prompt.
Inspect contents of your user directory, it should contain Desktop, Documents, etc. as shown below.

\begin{verbatim}
vfinley@alpha:~$ ls
Desktop  Documents  Downloads  Music  Pictures
  Public  snap  ssh  Templates  Videos
\end{verbatim}


