\section{Docker}
We eventually want to do our development in a developer container.
Before we can think about containers we need to install a container runtime on our alpha VM.

The easiest way to install a container runtime is to install either Docker or Podman.
Since much tooling was developed with Docker in-mind, Docker is the simplest to work with.
Podman is more secure, however mapping directories from the remote host to a rootless container can tricky.

When your remote host is Fedora/RHEL, you will probably use Podman.
Otherwise you will probably use Docker.

Since our alpha VM is running Ubuntu, we will install Docker.
Instructions to install Docker given by: \begin{verbatim}https://docs.docker.com/engine/install/ubuntu/#install-using-the-repository\end{verbatim} 
They are repeated here in case that webpage disappears.
To install Docker, at the VSCode Bash terminal connected to the alpha VM, do the following:
\begin{enumerate}
\item{Set up Docker's apt repository.}
\begin{verbatim}
# Add Docker's official GPG key:
sudo apt-get update
sudo apt-get install ca-certificates curl
sudo install -m 0755 -d /etc/apt/keyrings
sudo curl -fsSL https://download.docker.com/linux/ubuntu/gpg \
      -o /etc/apt/keyrings/docker.asc
sudo chmod a+r /etc/apt/keyrings/docker.asc

# Add the repository to Apt sources:
echo \
  "deb [arch=$(dpkg --print-architecture) \ 
  signed-by=/etc/apt/keyrings/docker.asc] \
  https://download.docker.com/linux/ubuntu \
  $(. /etc/os-release && \
  echo "${UBUNTU_CODENAME:-$VERSION_CODENAME}") stable" | \
  sudo tee /etc/apt/sources.list.d/docker.list > /dev/null
sudo apt-get update
\end{verbatim}

\item{Install the Docker packages.}
\begin{verbatim}
sudo apt-get install \
     docker-ce docker-ce-cli containerd.io docker-buildx-plugin \
     docker-compose-plugin
\end{verbatim}

\item{Verify that the installation is successful by running the hello-world image:}
\begin{verbatim}
sudo docker run hello-world
\end{verbatim}

\item{Add yourself or another user to the docker group}
\begin{verbatim}
# Add yourself to the docker group
# https://docs.docker.com/engine/install/linux-postinstall/

# Adding to docker group
sudo groupadd docker
sudo usermod -aG docker $USER
newgrp docker
docker run hello-world
\end{verbatim}
\end{enumerate}
